---
title: "TCG_FinalProject"
author: "Layeeq Mohammed & Pooja Awasthi"
date: "1 April 2019"
output: html_document
---

#We have chosen this data because of the following reason :
#This excessive rate of Energy consumption poses serious threats to the economic future of the United States. This data shows Energy Consumption of different states.
#It imports the most natural gas, which amounts for 110,000 billion metric meters.Therefore it is dependent on some other forms of 
#Energy such as hydroelectricity energy, nuclear energy, geothermal, solar energy consumption etc.
#At the end of the project we will be able to explain the use of different packages, how the data cleaning is done, regression model and exploartory data analysis.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(rvest)
library(plyr)
library(lubridate)
library(ggplot2)

urllink <- read.csv("https://raw.githubusercontent.com/poojaawasthi13/TCG_FinalProject/master/noniouzipcodes2015.csv",header=TRUE, sep=",")
data <- data.frame(urllink)
data


```

